---
title: "MMx Simulation and Optimization"
subtitle: v_`r if (!require(rjson)) {install.packages('rjson', dependencies = T, repos = "http://cloud.r-project.org/");};version=rjson::fromJSON(file = '../Source/Description.json')['version'];version` - (`r format(Sys.Date(), "%B %d, %Y")`)
author:
 - name: Scenario Report
output: 
  html_document:
    toc: true
    toc_float: true
    css : ../www/Styles/html_styles.css
  prettydoc::html_pretty:
    theme: cayman
    highlight: github
    css : ../www/Styles/pretty_styles.css
  pdf_document:
    toc: true
    toc_depth: 2
header-includes:
- \usepackage{fancyhdr}
- \usepackage{lipsum}
- \pagestyle{fancy}
- \fancyfoot[LE,RO]{\thepage}
- \fancypagestyle{plain}{\pagestyle{fancy}}
- \renewcommand{\footrulewidth}{0.4pt}
- \rhead{EDA Report for Data Frame}
- \fancyfoot[L]{`r version$version.string`}
- \fancyfoot[R]{`r format(Sys.time(), "%B %d %Y")`}

---


```{r, echo=FALSE}
# Read parameters passed to this function
reactData <- mmxRDS$reactData
histReactData <- mmxRDS$histReactData
adstock <- mmxRDS$adstock
input <- mmxRDS$input
reactDataOpt <- mmxRDS$reactDataOpt
mmxModel <- mmxRDS$mmxModel
scenarioTable <- mmxRDS$scenarioTable
scenarioList <- mmxRDS$scenarioList
viewScenario <- mmxRDS$viewScenario
runPanelNonPctContribution <- mmxRDS$runPanelNonPctContribution
runPanel <- mmxRDS$runPanel
runPanelHist <- mmxRDS$runPanelHist
histPanelNonPctContribution <- mmxRDS$histPanelNonPctContribution
runPanelAll <- mmxRDS$runPanelAll
compareScenario <- mmxRDS$compareScenario
allPctContribDataScenario1 <- mmxRDS$allPctContribDataScenario1
allPctContribDataScenario2 <- mmxRDS$allPctContribDataScenario2
allNonPctContribDataScenario1 <- mmxRDS$allNonPctContribDataScenario1
allNonPctContribDataScenario2 <- mmxRDS$allNonPctContribDataScenario2
allSalesDataScenario1 <- mmxRDS$allSalesDataScenario1
allSalesDataScenario2 <- mmxRDS$allSalesDataScenario2

```


```{r setup, include=FALSE}

tryCatch({
  knitr::opts_chunk$set(echo = FALSE, error=FALSE, warning = FALSE, fig.path = "../Downloads/temp/", comment = NA, fig.width=10, fig.height=6)
},error=function(e)
{
  print(paste0("Error : ",e))
})


loadPackage <- function(pkgName){
  
  if (!do.call(require, list(pkgName))) {
    install.packages(pkgName, dependencies = T, repos = "http://cran.us.r-project.org")
    do.call(library, list(pkgName))
  }
}

packages <- c('shiny',
              'shinydashboard',
              'shinyBS',
              'jsonlite',
              'scales',
              'DT',
              'tidyr',
              'ggplot2',
              'reshape',
              'purrr',
              'data.table',
              'rhandsontable',
              'formattable',
              'gdata',
              'tools',
              'nloptr',
              'dplyr'
              # 'plotly'
              # 'xlsx'
)

# sign_formatter <- formatter(
#   "span",
#   style = x ~ style(color = ifelse(x < 0 , "red", "green")),
#   x ~ icontext(ifelse(x < 0, "arrow-down", "arrow-up"), x))
# sign_formatter(c(-1, 0, 1))

#Importing all packages
lapply(packages, FUN = function(p){ loadPackage(p) })
  
  source('../www/MMX_Utils/Utils/adstock_decay_utility_functions.R')
  source('../www/MMX_Utils/Utils/simulation_utils.R')
  # source('./www/MMX_Utils/Utils/contribution_utility_function.R')
  #source('../www/MMX_Utils/Utils/contrib_marg_utility_functions.R')
  source('../www/MMX_Utils/Utils/customPrecision.R')

  mycat <- function(text){
    cat(gsub(pattern = "\n", replacement = "  \n", x = text))
  }

  
  
  # plot <- function(...,ncol=NULL,nrow=1){
  #   
  #   charts <- list(...)
  #   if(is.null(ncol)) ncol<- length(charts)
  #   
  #   if(is.null(charts[[1]])) return('Plot not available')
  #   if(length(charts)==0) return('Plot not available')
  #   if(any(class(charts) %in% c('gtable','grob'))) return(charts)
  #   
  #   charts$ncol=ncol
  #   charts$nrow=nrow
  #   do.call(grid.arrange,charts)
  # }
  
```

```{r}
htmltools::img(src = knitr::image_uri("../www/Logos/logo.png"), 
               alt = 'logo', 
               style = 'position:relative; float: right; margin-top: -125px; z-index:100;')

# htmltools::img(src = knitr::image_uri("../www/Logos/client_logo.png"), 
#                alt = 'logo', 
#                style = 'position:relative; float: right;height: 90px;width: 90px; margin-top: -125px; z-index:100;')
```

```{r go to top, results='asis',message=F}

#pander(reactData$summaryTable,style='rmarkdown')

#-----------------------------------------------------------------  Arrow  -------------------------------------------------------------------------#
htmltools::tags$a(href="#top",
htmltools::tags$i("",style="background: #ffffff;border-radius: 50%;display: block;height: 30px;width: 30px;-moz-border-radius: 50%;-webkit-border-radius: 50%;border: solid #C4BBB9;position: fixed; right: 15px; bottom :130px;"),
htmltools::tags$i("",style="border: solid #C4BBB9;border-width: 0 3px 3px 0;display: inline-block;padding: 3px;transform: rotate(-135deg);-webkit-transform: rotate(-135deg);position: fixed; right: 26px; bottom :143px;"),
htmltools::tags$i("",style="border: solid #C4BBB9;border-width: 0 3px 3px 0;display: inline-block;padding: 3px;transform: rotate(-135deg);-webkit-transform: rotate(-135deg);position: fixed; right: 26px; bottom :135px;"))
#---------------------------------------------------------------------------------------------------------------------------------------------------#

scrolLimit <- function(noOfRows){
  if(!is.null(noOfRows) && noOfRows<10){
    
    swe = paste(as.character(noOfRows*50),"px")
  }
  else{
    swe = "400px"
  }
  return(swe)
}
columnalign <- function(x) {
  columnclass <- lapply(x, class)
  return(unname(unlist(which(columnclass != "factor")-1)))
}

```

```{r load library, message=FALSE, warning=FALSE}

htmltools::tags$script("$(document).ready( function() {
  $('.toc-content').removeClass( 'col-md-9' );
} );
")


htmltools::tags$script("$(document).ready( function() {
  $('.toc-content').addClass( 'col-sm-12' );
} );
")
htmltools::tags$script("$(document).ready( function() {
  $('.toc-content').addClass( 'col-md-12' );
} );
")

htmltools::HTML('<h6 class=col-sm-4 style="left:0px;bottom:0px;width:20vw;position:fixed;">&copy; Copyright 2019 Mu Sigma Inc. All Rights Reserved</h6>')

htmltools::HTML('<script src="file:///./Source/jquery-1.7.1.min.js"></script>')

add=paste0(getwd(),"/toc-sticky-scroll-report.js")
htmltools::tags$script(src=add)

tryCatch({

pander::panderOptions('knitr.auto.asis', FALSE)

mycat <- function(text){
  cat(gsub(pattern = "\n", replacement = "  \n", x = text))
}
},error=function(e)
{
  print(paste0("Error : ",e))
})


```

`r if(!is.null(reactData$dataset)){"## Configurations"}` 

`r if(!is.null(reactData$dataset)){"### Loaded Historical Dataset"}`

```{r}
# library(dplyr)
if(!is.null(reactData$dataset) | nrow(reactData$dataset)>0){
  cat("The historical dataset (is the superset of train dataset) based on which the MMx model was built.\nSpend patterns will be decided based on this dataset.")
  nums <-  unlist(lapply(reactData$dataset, is.numeric)) 
  reactData$dataset[[reactData$DateVar]] <- as.Date(reactData$dataset[[reactData$DateVar]])
  DT::datatable(roundOffDataFrame(head(reactData$dataset),TRUE,2),options=list(scrollX=T, searching=FALSE, dom = 't'))%>% formatCurrency(colnames(reactData$dataset[nums]),currency = "", interval = 3, mark = ",")
}
# shiny::HTML(reactData$preprocessing_text)
```



`r if(!is.null(reactData$formula_report)){"### Loaded MMx Model"}`

```{r}
if(!is.null(reactData$formula_report)){
  cat("This is the MMX model object created in the modeling phase and display the inherent formula used to forecast the spends. This model object will be used to simulate results for the specified range of spends.\n")
  cat("Formula of the uploaded model object is \n")
  print(reactData$formula_report)
}

if(!is.null(mmxModel$train_data) | nrow(mmxModel$train_data)>0){

cat("Uploaded training dataset \n")
nums <-  unlist(lapply(mmxModel$train_data, is.numeric)) 
DT::datatable(roundOffDataFrame(head(mmxModel$train_data),TRUE,2),options=list(scrollX=T, searching=FALSE, dom = 't'))%>% formatCurrency(colnames(mmxModel$train_data[nums]),currency = "", interval = 3, mark = ",")
}

```

`r if(!is.null(reactData$preprocessing_text)){"### Selected Date Columns"}`
```{r}
if(!is.null(reactData$preprocessing_text)){
cat(reactData$preprocessing_text)
}
```

`r if(!is.null(reactData$spend_preprocessing)){"### Selected Spend, Panel and Target Columns"}`

```{r}
if(!is.null(reactData$spend_preprocessing)){
  cat(reactData$spend_preprocessing)
}

```


<!-- `r if(!is.null(reactData$loadDataSalesPlot)){"### Historical Data Plot"}` -->

```{r, eval=F}
if(!is.null(reactData$loadDataPanelVar)){
  cat(paste0('Selected panel : ', reactData$loadDataPanelVar))
}

if(!is.null(reactData$loadDataSalesPlot)){
  plot(reactData$loadDataSalesPlot)
}

```




```{r}
adstock<-mmxRDS$adstock
if(!is.null(adstock$dataset) | nrow(adstock$dataset)>0){
  cat(paste0('The underlying theory of adstock is that the exposure to advertising builds awareness in the consumer population, resulting in sales. Below are the mentioned optimal adstock values that have been considered for various channels while going about this exercise.'))
}
if(!is.null(adstock$dataset) | nrow(adstock$dataset)>0){
  nums <-  unlist(lapply(adstock$dataset, is.numeric)) 
  DT::datatable(roundOffDataFrame(head(adstock$dataset),TRUE,2),options=list(scrollX=T, searching=FALSE, dom = 't'))%>% formatCurrency(colnames(adstock$dataset[nums]),currency = "", interval = 3, mark = ",")
}

if(!is.null(input$viewAdstockPanelVar) & !is.null(input$viewAdstockChannelVar)){
  cat(paste0('Panel selected : ',input$viewAdstockPanelVar))
  cat(paste0('\nChannel selected : ',input$viewAdstockChannelVar))
}

if(!is.null(reactData$reportAdstockPlot)){
  plot(reactData$reportAdstockPlot)
}
  

```


`r if(!is.null(reactData$timePeriodPreprocessingText)){"### Selected Simulation/ Optimization Time Period"}`

```{r}
if(!is.null(reactData$timePeriodPreprocessingText)){
  mycat(reactData$timePeriodPreprocessingText)
}


```

`r if(nrow(histReactData$dataset)>0 & nrow(adstock$transformedDataset)>0){"### View Historical Comparison Period Performance {.tabset}"}`

```{r, eval=F}
if(!is.null(input$viewAdstockPanelVar)){
  shiny::h3('Summary')
cat(paste0('Panel selected : ',input$viewAdstockPanelVar))
}

```


<!-- `r if(nrow(histReactData$dataset)>0 & nrow(adstock$transformedDataset)>0){"### Time Series View {.tabset}"}` -->

```{r, results='asis'}
# if(!is.null(reactData$reportHistSalesSummary) & !is.null(reactData$reportHistSpendsSummary) & !is.null(reactData$reportHistPctSpendsSummary) & !is.null(reactData$reportHistContribSummary) & !is.null(reactData$reportHistContribPctSummary) & !is.null(reactData$reportHistROISummary)){
  
  
  if(!is.null(reactData$reportHistSalesSummary)){
    cat('\n\n')
  cat('#### Sales\n')
    plot(reactData$reportHistSalesSummary)
    cat('\n\n')
  }
  
  
  
  if(!is.null(reactData$reportHistSpendsSummary)){
    cat('\n\n')
  cat('#### Absolute Spends\n')
    plot(reactData$reportHistSpendsSummary)
    cat('\n\n')
  }
  
  
  
  
  if(!is.null(reactData$reportHistPctSpendsSummary)){
    cat('\n\n')
  cat('#### Percentage Spends\n')
    plot(reactData$reportHistPctSpendsSummary)
    cat('\n\n')
  }
  
  
  
  
  if(!is.null(reactData$reportHistContribSummary)){
    cat('\n\n')
  cat('#### Absolute Contribution\n')
    plot(reactData$reportHistContribSummary)
     cat('\n\n')
  }
  
 
  
  
  if(!is.null(reactData$reportHistContribPctSummary)){
    cat('\n\n')
    cat('#### Percentage Contribution\n')
    plot(reactData$reportHistContribPctSummary)
    cat('\n\n')
  }
  
  
  
  if(!is.null(reactData$reportHistROISummary)){
    cat('\n\n')
    cat('#### ROI\n')
    plot(reactData$reportHistROISummary)
    cat('\n\n')
  }
  
# }
```


`r if(length(scenarioList$files)>0){"## Simulated Scenarios"}`
```{r}
  if(!is.null(scenarioTable$dataset) | nrow(scenarioTable$dataset)>0){
    cat("Here one can view a list of saved feasible scenarios and one of them has been mentioned in detail for comparison or review by the client")
    shiny::h3('List of submitted scenarios')
    if(ncol(scenarioTable$dataset[unlist(lapply(scenarioTable$dataset, is.numeric))])==0){
      DT::datatable(roundOffDataFrame(scenarioTable$dataset, TRUE, 2), options=list(pagelength=6, scrollX=T, searching=FALSE, dom = 't'))
    }
    else{
    DT::datatable(roundOffDataFrame(scenarioTable$dataset, TRUE, 2), options=list(pagelength=6, scrollX=T, searching=FALSE, dom = 't'))%>%formatCurrency(colnames(scenarioTable$dataset[unlist(lapply(scenarioTable$dataset, is.numeric))]),currency = "", interval = 3, mark = ",")
    }
  }
```

`r if(length(scenarioList$files)>0){paste0("### ",reactData$viewScenarioSelected)}`

`r if(length(scenarioList$files)>0){"#### Simulated Spend Data {.tabset}"}`
```{r, results='asis'}
# if(!is.null(input$generateScenarioSelected)){
#   cat(paste0('Generated Scenario : ',input$generateScenarioSelected))
# }
# if(!is.null(input$viewGeneratedScenarioSelected)){
#   shiny::h3('View simulation spend data')
#   cat(paste0('Selected Scenario : ',input$viewGeneratedScenarioSelected))
# }
  
  if(!is.null(reactData$generatedScenarioData)){
    # cat('\n\n')
    # cat('### Tabular View\n')
    cat("This is a simulation dataset based on the variation parameter and spend strategy specified in the previous section.")
    nums <-  unlist(lapply(reactData$generatedScenarioData, is.numeric))
    DT::datatable(roundOffDataFrame(reactData$generatedScenarioData, TRUE, 2), options=list(scrollX=T, searching=TRUE, paging=TRUE))%>%formatCurrency(colnames(reactData$generatedScenarioData[nums]),currency = "", interval = 3, mark = ",")
    # cat('\n\n')
  }
  
```


<!-- `r if(length(scenarioList$files)>0){"#### Run Simulation"}` -->
```{r, eval=FALSE}
if(!is.null(input$runScenarioSelected)){
  cat(paste0('Scenario Run: ',input$runScenarioSelected))
}
```

<!-- `r if(!is.null(reactData$viewScenarioSelected) & !is.null(reactData$panelSelected)) {"#### View Simulation Results"}` -->
```{r, eval=F}
  
  if(!is.null(reactData$viewScenarioSelected) & !is.null(reactData$panelSelected)){
    cat(paste0('Scenario Selected: ',reactData$viewScenarioSelected))
    cat('\n')
    cat(paste0('Panel Selected: ',reactData$panelSelected))
    shiny::h4(paste0('Scenario Summary - ', reactData$viewScenarioSelected))
  }
  # if((!is.null(viewScenario$runScenarioResultsData) & !is.null(viewScenario$historicalScenarioDataWide)) |
  #   (nrow(viewScenario$runScenarioResultsData)>0 & nrow(viewScenario$historicalScenarioDataWide)>0)){
  

```

`r if(!is.null(reactData$simulationSalesPlot)) {"#### Simulation Summary {.tabset}"}`
```{r, results='asis'}
   if(!is.null(reactData$simulationSalesPlot)){
    cat('\n\n')
    cat('##### Sales\n')
    plot(reactData$simulationSalesPlot)
    cat('\n\n')
  }
  
  
  
  if(!is.null(reactData$simulationSpendAreaAbsPlot)){
    cat('\n\n')
    cat('##### Absolute Spends\n')
    plot(reactData$simulationSpendAreaAbsPlot)
    cat('\n\n')
  }
  
  
  
  if(!is.null(reactData$simulationSpendAreaPctPlot)){
    cat('\n\n')
    cat('##### Percentage Spends\n')
    plot(reactData$simulationSpendAreaPctPlot)
    cat('\n\n')
  }
  
  
  
  if(!is.null(reactData$simulationContributionAbsPlot)){
    cat('\n\n')
    cat('##### Absolute Contribution\n')
    plot(reactData$simulationContributionAbsPlot)
    cat('\n\n')
  }
  
    
  
  if(!is.null(reactData$simulationContributionPctPlot)){
    cat('\n\n')
    cat('##### Percentage Contribution\n')
    plot(reactData$simulationContributionPctPlot)
    cat('\n\n')
  }
  
  
  
  if(!is.null(reactData$simulationROIPlot)){
    cat('\n\n')
    cat('##### ROI\n')
    plot(reactData$simulationROIPlot)
    cat('\n\n')
  }
```


`r if(!is.null(reactData$salesSummaryPlot)) {"#### Simulation Period vs Historical Comparison Period (Summary) {.tabset}"}`
```{r, results='asis'}
  # shiny::h4(reactData$viewScenarioSelected)
  
  if(!is.null(reactData$salesSummaryPlot)){
    cat('\n\n')
    cat('##### Sales\n')
    plot(reactData$salesSummaryPlot)
    cat('\n\n')
  }
  
  

  
  if(!is.null(reactData$spendSummaryPlot)){
    cat('\n\n')
    cat('##### Spends\n')
    plot(reactData$spendSummaryPlot)
    cat('\n\n')
  }
  
  


  
  if(!is.null(reactData$contributionSummaryPlot)){
    cat('\n\n')
    cat('##### Contribution\n')
    plot(reactData$contributionSummaryPlot)
    cat('\n\n')
  }
  
  

  
  if(!is.null(reactData$ROISummaryPlot)){
    cat('\n\n')
    cat('##### ROI\n')
    plot(reactData$ROISummaryPlot)
    cat('\n\n')
  }
  
  
```


`r if(!is.null(reactData$salesTSOverlayPlot)) {"#### Simulation Period vs Historical Comparison Period (Time Series) {.tabset}"}`
```{r, results='asis'}
  
# if(nrow(runPanelNonPctContribution$dataset)>0 & nrow(runPanel$dataset_long)>0 & nrow(runPanelHist$dataset)>0 & nrow(histPanelNonPctContribution$dataset)>0 & nrow(runPanelAll$dataset)>0){
  if(!is.null(input$selectScenarioChannel)){
  shiny::h4(reactData$viewScenarioSelected)
  cat(paste0('Channel Selected: ', input$selectScenarioChannel))
  }
  
  if(!is.null(reactData$salesTSOverlayPlot)){
    cat('\n\n')
    cat('##### Sales Overlay\n')
    plot(reactData$salesTSOverlayPlot)
    cat('\n\n')
  }
  
  
  
  
  if(!is.null(reactData$salesTSPlot)){
    cat('\n\n')
    cat('##### Sales\n')
    plot(reactData$salesTSPlot)
    cat('\n\n')
  }
  
  

  
  if(!is.null(reactData$spendTSOverlayPlot)){
    cat('\n\n')
    cat('##### Spends Overlay\n')
    plot(reactData$spendTSOverlayPlot)
    cat('\n\n')
  }
  
  
  
  
  if(!is.null(reactData$spendTSPlot)){
    cat('\n\n')
    cat('##### Spends\n')
    plot(reactData$spendTSPlot)
    cat('\n\n')
  }
  
  
  
  
  if(!is.null(reactData$contributionTSOverlayPlot)){
    cat('\n\n')
    cat('##### Contribution Overlay\n')
    plot(reactData$contributionTSOverlayPlot)
    cat('\n\n')
  }
  
  
  
  
  if(!is.null(reactData$contributionTSPlot)){
    cat('\n\n')
    cat('##### Contribution\n')
    plot(reactData$contributionTSPlot)
    cat('\n\n')
  }
  
  
  
  
  if(!is.null(reactData$ROITSOverlayPlot)){
    cat('\n\n')
    cat('##### ROI Overlay\n')
    plot(reactData$ROITSOverlayPlot)
    cat('\n\n')
  }
  
  
  
  
  if(!is.null(reactData$ROITSPlot)){
    cat('\n\n')
    cat('##### ROI\n')
    plot(reactData$ROITSPlot)
    cat('\n\n')
  }
  
  
  
  # }
  
```

`r if(!is.null(input$selectedObjective)){"## Optimized Scenarios"}`

```{r, eval=F}
  # if(!is.null(reactData$opti_scenarioNameTable)){
  #   shiny::h3('List of submitted scenarios')
  #   DT::datatable(roundOffDataFrame(reactData$opti_scenarioNameTable, TRUE, 2), options=list(pagelength=6, scrollX=T, searching=FALSE, dom = 't')) %>%formatCurrency(colnames(reactData$opti_scenarioNameTable[unlist(lapply(reactData$opti_scenarioNameTable, is.numeric))]),currency = "", interval = 3, mark = ",")
  # }
if(!is.null(reactData$opti_scenarioNameTable)){
if(nrow(reactData$opti_scenarioNameTable)>0){
nums <-  unlist(lapply(reactData$opti_scenarioNameTable, is.numeric)) 
reactData$opti_scenarioNameTable[[reactData$DateVar]] <- as.Date(reactData$opti_scenarioNameTable[[reactData$DateVar]])
DT::datatable(roundOffDataFrame(head(reactData$opti_scenarioNameTable),TRUE,2),options=list(scrollX=T, searching=FALSE, dom = 't'))%>% formatCurrency(colnames(reactData$opti_scenarioNameTable[nums]),currency = "", interval = 3, mark = ",")
}}
```

`r if(!is.null(input$selectedObjective)){paste0("###", input$chooseOptiScenario)}`

`r if(!is.null(input$selectedObjective)){paste0("#### " ,"Selected Business Priority: ", input$selectedObjective)}`


<!-- `r if(!is.null(input$budgetPercent) & !is.null(reactData$optimisedBudget)){"#### Define Constraints"}` -->

```{r}
# shiny::br()
# shiny::HTML('The 
# <ul><li>Cool</li>
# <li>Maximize ROI option gives user an option to maximize the return under given spends constraint</li>
# <li>Revenue Chase option can be used for optimizing spends to achieve a target revenue</li>
# </ul>')
if(!is.null(input$budgetPercent)){
mycat(paste0("Historical Budget: $", format(round(reactData$budget), big.mark = ","),"\n"))
# shiny::br()
mycat(paste0("Incremental Budget (%): ", input$budgetPercent,"\n"))
# shiny::br()

mycat(paste0("New Budget: $", format(round(reactData$optimisedBudget), big.mark = ","),"\n"))
}

if(!is.null(input$budgetPercent)){
  nums <-  unlist(lapply(reactData$constraint, is.numeric)) 
  if(any(nums==TRUE)){
  mycat('Entered Constraints')
  DT::datatable(reactData$constraint,options=list(scrollX=T, pagelength=10))%>% formatCurrency(colnames(reactData$constraint[nums]),currency = "", interval = 3, mark = ",")
  }
  else{
    mycat('Entered Constraints')
  DT::datatable(reactData$constraint,options=list(scrollX=T, pagelength=10))
  }
}

if(!is.null(input$budgetPercent)){
  mycat('Entered Channel Bounds')
  nums <-  unlist(lapply(reactData$bound, is.numeric)) 
  DT::datatable(reactData$bound,options=list(scrollX=T, pagelength=10))%>% formatCurrency(colnames(reactData$bound[nums]),currency = "", interval = 3, mark = ",")
}

if(!is.null(input$selectedTechnique)){
mycat(paste0('Selected Optimization Technique : "', input$selectedTechnique,'"\n'))
mycat(paste0("The optimized value for the Business Objective '", input$selectedObjective, "' is: US($)", reactData$optimal_value, "\n",reactData$final_message))
}

```



<!-- `r if(!is.null(input$choosePanel)){"#### View Optimization Results"}` -->

`r if(!is.null(input$choosePanel)){"##### Optimization Summary {.tabset}"}`
```{r, results='asis'}

#################################################################################################
  
  if(!is.null(reactData$reportSalesSummary)){
    cat('\n\n')
    cat('###### Total Sales\n')
    plot(reactData$reportSalesSummary)
    cat('\n\n')
  }

  if(!is.null(reactData$reportallSalesSummary)){
    cat('\n\n')
    cat('###### All Sales\n')
    plot(reactData$reportallSalesSummary)
    cat('\n\n')
  }
  
  
  if(!is.null(reactData$reportSpendsSummary)){
    cat('\n\n')
    cat('###### Absolute Spends\n')
    plot(reactData$reportSpendsSummary)
    cat('\n\n')
  }

  if(!is.null(reactData$reportpctSpendsSummary)){
    cat('\n\n')
    cat('###### Percentage Spends\n')
    plot(reactData$reportpctSpendsSummary)
    cat('\n\n')
  }
  
  
  if(!is.null(reactData$reportContributionSummary)){
    cat('\n\n')
    cat('###### Absolute Contribution\n')
    plot(reactData$reportContributionSummary)
    cat('\n\n')
  }
  
  
    
  
  if(!is.null(reactData$reportpctContributionSummary)){
    cat('\n\n')
    cat('###### Percentage Contribution\n')
    plot(reactData$reportpctContributionSummary)
    cat('\n\n')
  }
  
  
  
  
  if(!is.null(reactData$reportROISummary)){
    cat('\n\n')
    cat('###### ROI\n')
    plot(reactData$reportROISummary)
    cat('\n\n')
  }
  
  

```

`r if(!is.null(input$choosePanel)){"##### Optimization Comparison {.tabset}"}`
```{r, results='asis'}
##################################################################################################

  
  if(!is.null(reactData$reportSalesSC)){
  cat('\n\n')
  cat('###### Sales\n')
  plot(reactData$reportSalesSC)
  cat('\n\n')
}
  
  

  
  if(!is.null(reactData$reportSpendsSC)){
  cat('\n\n')
  cat('###### Spends\n')
  plot(reactData$reportSpendsSC)
  cat('\n\n')
}
  
  


  
  if(!is.null(reactData$reportContributionSC)){
  cat('\n\n')
  cat('###### Contribution\n')
  plot(reactData$reportContributionSC)
  cat('\n\n')
}
  
  

  
  if(!is.null(reactData$reportROISC)){
  cat('\n\n')
  cat('###### ROI\n')
  plot(reactData$reportROISC)
  cat('\n\n')
}
  
  

###################################################################################################
```

`r if(!is.null(input$choosePanel)){"##### Optimization Time-Series Comparison {.tabset}"}`
```{r, results='asis'}

  
  if(!is.null(reactData$reportSalesTS)){
    cat('\n\n')
    cat('###### Sales Overlay\n')
    plot(reactData$reportSalesTS)
    cat('\n\n')
  }
  
  
  
  
   if(!is.null(reactData$reportSalesContinuousTS)){
    cat('\n\n')
    cat('###### Sales\n')
    plot(reactData$reportSalesContinuousTS)
    cat('\n\n')
  }
  
  


   if(!is.null(reactData$reportSpendsTS)){
    cat('\n\n')
    cat('###### Spends Overlay\n')
    plot(reactData$reportSpendsTS)
    cat('\n\n')
  }
  
  
  
  
   if(!is.null(reactData$reportSpendsContinuousTS)){
    cat('\n\n')
    cat('###### Spends\n')
    plot(reactData$reportSpendsContinuousTS)
    cat('\n\n')
  }
  
  
  
  
   if(!is.null(reactData$reportContributionTS)){
    cat('\n\n')
    cat('###### Contribution Overlay\n')
    plot(reactData$reportContributionTS)
    cat('\n\n')
  }
  
  
  
  
   if(!is.null(reactData$reportContributionContinuousTS)){
    cat('\n\n')
    cat('###### Contribution\n')
    plot(reactData$reportContributionContinuousTS)
    cat('\n\n')
  }
  
  
  
  
   if(!is.null(reactData$reportROITS)){
    cat('\n\n')
    cat('###### ROI Overlay\n')
    plot(reactData$reportROITS)
    cat('\n\n')
  }
  
  
  
  
   if(!is.null(reactData$reportROIContinuousTS)){
    cat('\n\n')
    cat('###### ROI\n')
    plot(reactData$reportROIContinuousTS)
    cat('\n\n')
  }
  
  
```

`r if(!is.null(compareScenario$histScenario1Wide) & !is.null(compareScenario$histScenario2Wide) & !is.null(compareScenario$runScenario1Wide) & !is.null(compareScenario$runScenario2Wide)){"## Compare Scenarios"}`
```{r, results='asis'}
if(!is.null(adstock$compareScenarioList)){
shiny::h4("Select Scenarios")
cat(paste0('Scenarios selected for comparison: ', adstock$compareScenarioList))
cat('\n')
}
if(!is.null(reactData$CSPanelSelected)){
  cat(paste0('Panel Selected: ', reactData$CSPanelSelected))
}


if(!is.null(compareScenario$histScenario1Wide) & !is.null(compareScenario$histScenario2Wide) & !is.null(compareScenario$runScenario1Wide) & !is.null(compareScenario$runScenario2Wide)){
  if(nrow(compareScenario$histScenario1Wide)>0 & nrow(compareScenario$histScenario2Wide)>0 & nrow(compareScenario$runScenario1Wide)>0 & nrow(compareScenario$runScenario2Wide)>0){
  
  shiny::h3("Tabular View")
  nums <-  unlist(lapply(reactData$compareScenarioTable, is.numeric))
  DT::datatable(roundOffDataFrame(reactData$compareScenarioTable,TRUE,2),options=list(scrollX=T, searching=TRUE, paging=TRUE))%>%                              formatCurrency(colnames(reactData$compareScenarioTable[nums]),currency = "", interval = 3, mark = ",")
}}


```


`r if(!is.null(reactData$scenarioSalesHistPlot)){"### Summary View {.tabset}"}`
```{r, results='asis'}
  
  if(!is.null(reactData$scenarioSalesHistPlot) & !is.null(reactData$scenarioSalesSimPlot)){
    cat('\n\n')
    cat('#### Sales\n')
    plot(reactData$scenarioSalesHistPlot)
    plot(reactData$scenarioSalesSimPlot)
    cat('\n\n')
  }
  
  
  
  
  
   if(!is.null(reactData$scenarioSpendHistPlot) & !is.null(reactData$scenarioSpendSimPlot)){
    cat('\n\n')
    cat('#### Spends\n')
    plot(reactData$scenarioSpendHistPlot)
    plot(reactData$scenarioSpendSimPlot)
    cat('\n\n')
  }
  
  
  
  
  
   if(!is.null(reactData$scenarioContributionHistPlot) & !is.null(reactData$scenarioContributionSimPlot)){
    cat('\n\n')
    cat('#### Contribution\n')
    plot(reactData$scenarioContributionHistPlot)
    plot(reactData$scenarioContributionSimPlot)
    cat('\n\n')
  }
  

  
  
  
  
   if(!is.null(reactData$scenarioROIHistPlot) & !is.null(reactData$scenarioROISimPlot)){
    cat('\n\n')
    cat('#### ROI\n')
    plot(reactData$scenarioROIHistPlot)
    plot(reactData$scenarioROISimPlot)
    cat('\n\n')
  }

  
  
```

`r if(!is.null(reactData$salesCSTSplot)){"### Time Series View {.tabset}"}`

```{r, results='asis'}
# if(nrow(allPctContribDataScenario1$dataset)>0 & nrow(allPctContribDataScenario2$dataset)>0 & nrow(allNonPctContribDataScenario1$dataset)>0 & nrow(allNonPctContribDataScenario2$dataset)>0 & nrow(allSalesDataScenario1$dataset)>0 & nrow(allSalesDataScenario2$dataset)>0){
  
  
   if(!is.null(reactData$salesCSTSplot)){
    cat('\n\n')
    cat('#### Sales\n')
    plot(reactData$salesCSTSplot)
    cat('\n\n')
  }
  
  

  
   if(!is.null(reactData$spendsCSTSplot)){
    cat('\n\n')
    cat('#### Spends\n')
    plot(reactData$spendsCSTSplot)
    cat('\n\n')
  }
  
 


  
   if(!is.null(reactData$contribCSTSplot)){
    cat('\n\n')
    cat('#### Contribution\n')
    plot(reactData$contribCSTSplot)
    cat('\n\n')
  }
  
  

  
   if(!is.null(reactData$roiCSTSPlot)){
    cat('\n\n')
    cat('#### ROI\n')
    plot(reactData$roiCSTSPlot)
    cat('\n\n')
  }
  
  

# }
```
